---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mountainmathHelpers

<!-- badges: start -->
[![Build Status](https://travis-ci.org/mountainMath/mountainmathHelpers.svg?branch=master)](https://travis-ci.org/mountainMath/mountainmathHelpers)
<!-- badges: end -->

MountainmathHelpers is a collection of helper functions that are frequently used at MountainMath. This package
can be used to access these functions, be it for reproducing and running code written by MountianMath or
because they happen to be useful for whatever code others are writing.

## Installation

You can install the development version from [GitHub](https://github.com/mountainMath/mountainmathHelpers) with:

``` r
remotes::install_github("mountainMath/mountainmathHelpers")
```


## Vector tile example

It can be cumbersome to add nice background layers in ggplot maps. The `rmapzen` package provides convenient access to former Mapzen vector tiles, now hosted via NextZen. This package adds several `geom_xxx` functions to autmoatically fetch relevant vector tile data and add them to a map. 

Here is an example how to add water and road vector layers.

```{r}
library(mountainmathHelpers)
library(cancensus)
library(ggplot2)

data <- get_census("CA16",regions=list(CSD="5915022"),level="CT",geo_format="sf",
                   vectors=c("lico"="v_CA16_2570"))

ggplot(data) +
  geom_sf(aes(fill=lico/100),size=0.1) +
  scale_fill_viridis_c(labels=scales::percent) +
  geom_water() +
  geom_roads() +
  coord_bbox(sf::st_bbox(data)) +
  labs(title="Share of people in low income (LICO-AT)",fill=NULL)
```

